Two Mode Networks and Relational Similarity

### 2024-03-29 analysis.qmd
ncsu presentation

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(cowplot)
   library(here)
   library(patchwork)
   library(dplyr)
   library(factoextra)
   library(ggbump)
   library(ggcorrplot)
   library(ggplot2)
   library(ggpubr)
   library(ggrepel)
   library(igraph)
   library(patchwork)
   source(here("Functions", "TwoModeCA.R"))
   source(here("Functions", "TwoModeSR.R"))
   source(here("Functions", "reflections.R"))
   source(here("Functions", "ref.long.dat.R"))
```

@@

          0, 0, 0, 0, 0,  1, 0, 1, 1,  0, 0, 0, 0, 0,
          0, 0, 0, 0, 0,  0, 0, 1, 1,  0, 0, 0, 0, 0),
          ncol = 14, byrow = TRUE)
     w <- c("EVELYN", "LAURA", "THERESA", "BRENDA", "CHARLOTTE", "FRANCES", "ELEANOR", "RUTH", "VERNE", "MYRA", "KATHERINE", "SYLVIA", "NORA", "HELEN", "OLIVIA", "FLORA", "PEARL", "DOROTHY")
     e <- paste("E", c(1:14), sep = "")
     rownames(A) <- w
     colnames(A) <- e
```

@@

   # fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p1 <- p + scale_color_manual(values=as.vector(cols25(18)))

   plot.dat <- b$group$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = group))
   #geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 1)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 24), 
                              aes(x = n.iter, label = group), 
                              size = 4, nudge_x = -2)
   p <-    p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = group), 
                                    size = 4, nudge_x = -1)
   #fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p2 <- p + scale_color_manual(values=as.vector(cols25(15)))
   png(file = here("Plots", "pg-reflections.jpg"), width=750, height=950)
   p1 / p2
   dev.off()
```

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   a <- TwoModeCA(A)
   b <- a$ca.A
   c <- a$bon.A
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
   dev.off() 
```

```{r CA Eigenvector Plot}
    tmCA.res <- TwoModeCA(A, k.r = 2, k.c = 2)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    png(file = here("Plots", "ca-eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

@@

    png(file = here("Plots", "ca-sim.png"), width=950, height=700)
      (a | b) / c + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20)) 
    dev.off() 
```

>>>>

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(cowplot)
   library(here)
   library(patchwork)
   library(dplyr)
   library(factoextra)
   library(ggbump)
   library(ggcorrplot)
   library(ggplot2)
   library(ggpubr)
   library(ggrepel)
   library(igraph)
   library(pals)
   library(patchwork)
   source(here("Functions", "TwoModeCA.R"))
   source(here("Functions", "TwoModeSR.R"))
   source(here("Functions", "reflections.R"))
   source(here("Functions", "ref.long.dat.R"))
```

@@

          0, 0, 0, 0, 0,  1, 0, 1, 1,  0, 0, 0, 0, 0,
          0, 0, 0, 0, 0,  0, 0, 1, 1,  0, 0, 0, 0, 0),
          ncol = 14, byrow = TRUE)
     w <- c("EVELYN", "LAURA", "THERESA", "BRENDA", "CHARLOTTE", "FRANCES", "ELEANOR", "RUTH", "VERNE", "MYRNA", "KATHERINE", "SYLVIA", "NORA", "HELEN", "OLIVIA", "FLORA", "PEARL", "DOROTHY")
     e <- paste("E", c(1:14), sep = "")
     rownames(A) <- w
     colnames(A) <- e
```

@@

   # fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p1 <- p + scale_color_manual(values=as.vector(cols25(18)))
   png(file = here("Plots", "p-reflections.png"), width=750, height=500)
   p1
   dev.off()

   plot.dat <- b$group$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = group))
   #geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 1)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 24), 
                              aes(x = n.iter, label = group), 
                              size = 4, nudge_x = -2)
   p <-    p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = group), 
                                    size = 4, nudge_x = -1)
   #fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p2 <- p + scale_color_manual(values=as.vector(cols25(15)))
   png(file = here("Plots", "g-reflections.png"), width=750, height=500)
   p2
   dev.off()
   png(file = here("Plots", "pg-reflections.png"), width=750, height=950)
   p1 / p2
   dev.off()
```

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   a <- TwoModeCA(A)
   b <- a$ca.A
   c <- a$bon.A
   png(file = here("Plots", "ca-reord.png"), width=500, height=500)
   b
   dev.off() 
   png(file = here("Plots", "bon-reord.png"), width=500, height=500)
   c
   dev.off() 
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
   dev.off() 
```

```{r CA Eigenvector Plot}
    tmCA.res <- TwoModeCA(A, k.r = 2, k.c = 2)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)

   png(file = here("Plots", "ca-eigvec-p.png"), width=500, height=500)
   a
   dev.off() 
   png(file = here("Plots", "ca-eigvec-g.png"), width=500, height=500)
   b
   dev.off() 
    png(file = here("Plots", "ca-eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

@@

    png(file = here("Plots", "ca-sim.png"), width=950, height=700)
      (a | b) / c + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20)) 
    dev.off() 
    png(file = here("Plots", "ca-sim-slide.png"), width=1050, height=700)
      (a | b) / c + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20)) 
    dev.off() 
```
